Supplemental material for: Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management

### 2021-11-29 Scripts/Supplements.Rmd
Updates supplemental figures

@@

```{r toeFigureS9, eval = T,  echo = F, fig.width=7, fig.height=5, fig.cap = "Changes in stock proportion of neighboring Exclusive Economic Zones of Latin America and the Caribeen and Northwestern Europe by 2030 (2021-2040) and by 2060 (2041-2060) relative to 1951-2005. Lines represent the average change in transboundary stock share ratio (Methods) with arrows going from EEZ with decreasing stock share (point) to those gaining shares (arrowhead). Land polygons represent the percentage of stocks that are projected to change their stock share ratio (i.e., over two standard deviations from the historical catch proportion) beyond the identified threat point with higher gains identified in warmer colors.}

@@

```{r toeFigureS10, eval = T,  echo = F, fig.width=7, fig.height=5, fig.cap = "Changes in the stock share proportion of top 5 most valuable stocks by 2030 (2021-2040) relative to 1951-2005. Lines represent the average change in transboundary stock share ratio (Methods) with arrows going from EEZ with decreasing stock share (point) to those gaining shares (arrowhead).}

>>>>

```{r toeFigureS5, eval = T,  echo = F, fig.width=7, fig.height=5, fig.cap = "Year of change in the shared distribution of transboundary stocks in the Caribbean and South Pacific Islands. Land polygons show the contribution of shifting stocks to a country or territory’s total fishing revenue from transboundary stocks. Exclusive Economic Zone polygons display average year of range shifts within them. Warm colors are indicative of an early shift/high fishing revenue contribution from transboundary stocks while cold colors represent a late shift/low fishing revenue. EEZs with no distributional shift between 2006 and 2100 are represented in pale blue."}

img <- readPNG("../Figures/FigS11.png")
grid.raster(img)

@@

```{r toeFigureS9, eval = T,  echo = F, fig.width=7, fig.height=5, fig.cap = "Changes in stock proportion of neighboring Exclusive Economic Zones of Latin America and the Caribeen and Northwestern Europe by 2030 (2021-2040) and by 2060 (2041-2060) relative to 1951-2005. Lines represent the average change in transboundary stock share ratio (Methods) with arrows going from EEZ with decreasing stock share (point) to those gaining shares (arrowhead). Land polygons represent the percentage of stocks that are projected to change their stock share ratio (i.e., over two standard deviations from the historical catch proportion) beyond the identified threat point with higher gains identified in warmer colors."}

@@

```{r toeFigureS10, eval = T,  echo = F, fig.width=7, fig.height=5, fig.cap = "Changes in the stock share proportion of top 5 most valuable stocks by 2030 (2021-2040) relative to 1951-2005. Lines represent the average change in transboundary stock share ratio (Methods) with arrows going from EEZ with decreasing stock share (point) to those gaining shares (arrowhead)."}
